fl0w 2.0 - a development environment for the\\ KIPR Wallaby

### 2017-03-16 paper.tex
Add reference to Boostrap 3

\subsection{dashb0ard}
dashb0ard is a single-page web front-end designed to manage the fl0w fleet. It can be used to configure connected controllers and obtain sensor readouts as well as debug logs. It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Bootstrap 3 as a design baseline, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.

@@

\bibitem{watchdog:Yesudeep Mangalapilly}
Yesudeep Mangalapilly, \emph{watchdog}, \url{https://github.com/gorakhargosh/watchdog}, \\ source code, accessed February 9th 2017

>>>>

\subsection{dashb0ard}
dashb0ard is a single-page web front-end designed to manage the fl0w fleet. It can be used to configure connected controllers and obtain sensor readouts as well as debug logs. It utilities the JavaScript version of undergr0und to retrieve data from fl0w, Vue.js for its user interface, Bootstrap 3\cite{Bootstrap 3:Twitter Inc.} as a design baseline, Charts.js to display graphs and jQuery\cite{jQuery:jQuery Foundation} for additional DOM manipulation.

@@

\bibitem{Bootstrap 3:Twitter Inc.}
Twitter, Inc., \emph{Bootstrap 3}, \url{http://getbootstrap.com},\\ product page,
accessed March 16th 2017
